\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-04-26 Tex/paper.tex

\begin{table}[htp]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Terms} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Total Number Cases} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Cases/Term} \\ \hline
CE Hughes*              & 1937 - 1941                                          & 628                                                               & 125.6                                                     \\ \hline
HF Stone                & 1942 - 1946                                          & 756                                                               & 151.2                                                     \\ \hline
FM Vinson               & 1946 - 1953                                          & 789                                                               & 98.63                                                      \\ \hline
E Warren                & 1954 - 1969                                          & 2149                                                              & 126.41                                                     \\ \hline
WE Burger               & 1970 - 1986                                          & 2805                                                             & 155.83                                                     \\ \hline
W Rehnquist            & 1987 - 2005                                          & 2022                                                              & 106.42                                                      \\ \hline
J Roberts **           & 2006 - 2015                                          & 796                                                              & 79.6                                           \\ \hline
\end{tabular}
\caption[caption]{For the time range of interest (1937 - 2015) this table displays the chief justices, the time range they served as chief justice, the number of cases in their time range as well as the average number of cases per year.\\\hspace{\textwidth} * CE Hughes served as chief justice from 1930 - 1941. \\\hspace{\textwidth} ** J Roberts still serves as chief justice (retrieved 3/2018).}
\label{tab:chiefs}
\end{table}

@@

 (k) Overruled Cases &  \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/overruled_coef_trend_linear.pdf} &  \\

>>>>

\begin{table}[htp]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Terms} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Total Number Cases} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Cases/Term} \\ \hline
CE Hughes*              & 1937 - 1941                                          & 628                                                               & 125.6                                                     \\ \hline
HF Stone                & 1942 - 1946                                          & 756                                                               & 151.2                                                     \\ \hline
FM Vinson               & 1946 - 1953                                          & 789                                                               & 98.63                                                      \\ \hline
E Warren                & 1954 - 1969                                          & 2149                                                              & 126.41                                                     \\ \hline
WE Burger               & 1970 - 1986                                          & 2805                                                             & 155.83                                                     \\ \hline
W Rehnquist            & 1987 - 2005                                          & 2022                                                              & 106.42                                                      \\ \hline
J Roberts **           & 2006 - 2015                                          & 796                                                              & 79.6                                           \\ \hline
\end{tabular}
\caption[caption]{For the time range of interest (1937 - 2015) this table displays the chief justices, the time range they served as chief justice, the number of cases in their time range as well as the average number of cases per year.\\\hspace{\textwidth} * CE Hughes served as chief justice from 1930 - 1941. \\\hspace{\textwidth} ** J Roberts still serves as chief justice (retrieved 4/2018).}
\label{tab:chiefs}
\end{table}

@@

 (k) Overruled Cases & (l) Justice Homophily \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/overruled_coef_trend_linear.pdf} & 
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/justicehomophily_coef_trend_linear.pdf} \\
